The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
rm editors

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
  # github_document
  bookdown::pdf_document2:
     number_sections: true
     toc: false
  # bookdown::word_document2:
  #   reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or associations to
occur individuals must share space, and thus have overlapping home ranges
[@Vander_Wal_2013]. In the context of the social environment, home range overlap
is an example of how animals share space over coarser spatial and temporal
scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly
scales spatially and temporally, it remains unclear whether coarser scales of
sociality, including social association and home range overlap, vary predictably
with social interaction [@Castles_2014;
@Farine_2015a]. Thus, we define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a]. <!--
Farine references comes out as D.R. Farine 2015 -->

>>>>

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
  # github_document
  bookdown::pdf_document2:
     number_sections: true
     toc: false
  # bookdown::word_document2:
  #   reference_docx: template.docx
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social association
represents shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or associations to
occur individuals must share space, and thus have overlapping home ranges
[@Vander_Wal_2013]. In the context of the social environment, home range overlap
is an example of how animals share space over coarser spatial and temporal
scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly
scales spatially and temporally, it remains unclear whether coarser scales of
sociality, including social association and home range overlap, vary predictably
with social interaction [@Castles_2014;
@Farine_2015a]. Thus, we define social scale as the type of social relationship
observed that can be explicitly defined and measured [@Farine_2015a].
